Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
phrs

\section{Introduction}
A key goal in improving patient-clinician communication is
establishing a common context for communication with which a shared
understanding can be established.  This understanding is
bi-directional, in the sense that the patient needs to be able to
effectively interpret what the clincian is trying to convey to him or
her, but also that the clinician needs to be able to arrive at an
accurate characterisation of the patient's situation and condition, as
updated since the patient was last seen, often under time pressure and
other constraints.

@@

Yet, so far, EHRs have primarily been limited to the storage of
official diagnoses and diagnostic reports prepared by clinicians,
technicians and nurses.  These communications are both highly
technical, making them difficult to interpret by end-user patients,
but also highly limited in temporal resolution, reflecting only cases
where a person was attended to and diagnostic-tested by a medical
professional.  Although this may be frequent for patients in inpatient
care, those that come to see their clinician, say, once a month end up
with extremely low-resolution views of a patient's condition.

>>>>

\section{Introduction}
A key goal in improving patient-clinician communication is
establishing a common context for communication with which a shared
understanding can be established.  This understanding is
bi-directional, in the sense that the patient needs to be able to
effectively interpret what the clincian is trying to convey to him or
her, but also that the clinician needs to be able to arrive at an
accurate characterisation of the patient's situation and condition, as
updated since the patient was last seen. This is often under time
pressure and with limited access to information about how the patient
has been in the interim.

@@

Yet, so far, EHRs have primarily been limited to the storage of
official diagnostic reports prepared by clinicians, technicians and
nurses.  These communications are both highly technical, making them
difficult to interpret by end-user patients, but also highly limited
in temporal resolution, reflecting only cases where a person was
attended to and diagnostic-tested by a medical professional.  Although
this may be frequent for patients in inpatient care, those that come
to see their clinician, say, once a month end up with extremely
low-resolution views of a patient's condition.
